Capturing Policies for BYOD

### 2016-10-21 paper.tex
updates

We analysed five different policies to find common idioms.
The first is the \emph{Security Policy Template: Use of Handheld Devices in a Corporate Environment}, published by the SANS Institute~\cite{nicholas_r._c._guerin_security_2008}.
This is a hypothetical policy published to help companies mitigate the threats to corporate assets caused by mobile devices. 
Companies are expected to modify the document to suit their needs.  The policy is general; not specific to any particular industry, device, or country's legislation.

The second is taken from HiMMS.

>>>>

We analysed five different policies to find common idioms.
The first is the \emph{Security Policy Template: Use of Handheld Devices in a Corporate Environment}, published by the SANS Institute~\cite{nicholas_r._c._guerin_security_2008}.
This is a hypothetical policy published to help companies mitigate the threats to corporate assets caused by mobile devices. 
Companies are expected to modify the document to suit their needs.  The policy is general; not specific to any particular industry, device, or country's legislation.
The second is taken from Healthcare Information Management System Society~\cite{healthcare_information_and_management_systems_society_mobile_2012}; a US non-profit company trying to improve healthcare through IT.  
The policy is designed as a sample agreement for a system trying to manage personal mobile devices in a healthcare environment.
The third is taken from an british hospital trust~\cite{kennington_mobiles_2014}, and describes the BYOD scheme used in practice at the hospital. 
Finally two simpler policies are taken from Edinburgh university~\cite{david_williamson_bring_2015} and a company specialising in emergency sirens~\cite{code3pse.org_sample_????}. 
These policies are simpler than the other comprised of much more general rules and only a page or two in length.
